Exception Handling Bug Hazards in Android

### 2015-10-11 SPRINGER_JOURNAL/msr_journal.tex
Included some qualitative findings in the conclusion.
Sharpened the conclusion a bit, most notably to establish the
link between the empirical and qualitative studies.

Also included main *outcomes* of the qualitative study.

The goal of this paper is two-fold: (i) to investigate 
to what extent stack trace information can reveal \emph{bug hazards} 
related to exception handling code that may lead to a decrease in
application robustness; and (ii) to assess the developers' perspective
concerning the detected EH \emph{bug hazards}.

To that end, we mined the stack 
traces embedded in all issues defined in 482 Android projects hosted on GitHub and 
157 projects hosted on Google Code -- overall considering 6,005
exception stack traces. We also surveyed developers associated with some of 
the mined GitHub projects.
Our first key contribution is
a novel approach and toolset (ExceptionMiner) for analyzing Java
  exception stack traces as occurring in GitHub and Google Code
  issues.
Our second contribution is
an empirical study of over 6000 actual stack traces,
  demonstrating that (1) half of the system crashes are due to errors
  in programming logic, with null pointer exceptions being most
  prominent;
  (2) documentation for explicitly thrown RuntimeExceptions is almost
  never provided; 
  (3) extensive use of wrapping leads to hard-to-understand chains
  violating Java's exception handling principles.
Our third contribution was the first exploratory study to assess the 
developers' perspective concerning the exception handling 
bug hazards in Android development.
 Our results shed light on common problems and bug hazards in Java
exception handling code, and call for tool support to help developers
understand their own and third party exception handling and wrapping logic.

>>>>

The goal of this paper is two-fold: (i) to investigate 
to what extent stack trace information can reveal \emph{bug hazards} 
related to exception handling code that may lead to a decrease in
application robustness; and (ii) to assess the developers' perspective
concerning the detected exception handling bug hazards.

To realize this goal, we mined the stack 
traces embedded in all issues defined in 482 Android projects hosted on GitHub and 
157 projects hosted on Google Code -- overall considering 6,005
exception stack traces. We subsequently surveyed developers associated with 
a selection of 
the mined GitHub projects.

Our first key contribution is
a novel approach and toolset (ExceptionMiner) for analyzing Java
  exception stack traces as occurring in GitHub and Google Code
  issues.

Our second contribution is
an empirical study of over 6000 actual stack traces,
  demonstrating that:
\begin{enumerate} 
  \item Half of the system crashes are due to errors
  in programming logic, with null pointer exceptions being most
  prominent;
  \item Documentation for explicitly thrown RuntimeExceptions is almost
  never provided; 
  \item Extensive use of wrapping leads to hard-to-understand chains
  violating Java's exception handling principles.
\end{enumerate}

Our third contribution is a qualitative study to assess the 
developers' perspective concerning the exception handling 
bug hazards in Android development.
This study corroborates the findings of our stack trace analysis, most notably the prevalence
of null pointer exceptions and the reliability implications of (in particular cross-type) wrappings.
Furthermore, we found that few developers are aware of the undocumented checked exceptions signaled by native C code of the Android platform.

In conclusion, our findings shed light on common problems and bug hazards in Java
exception handling code, and call for tool support to help developers
understand their own and third party exception handling and wrapping logic.
